\documentclass[letter]{res}

\setlength{\textheight}{9.5in}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=10mm,
 right=20mm,
 top=15mm,
 bottom=5mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{url}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}


\begin{document}

\name{Shubham Srivastava\\[20pt]}
\address{
  \texttt{\url{www.github.com/shbm}}
  } 
\address{
  \texttt{shbm09@gmail.com}\\
  \texttt{(+91) 7571 998541}\\
  } 
\begin{resume}
  \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.1pt}}

\section{Skills}
{\sl \textbf{Programming Languages:}}  Python(proficient), C++(proficient), JavaScript(proficient), C (proficient), Java, Go\\
{\sl \textbf{Operating Systems:}} Linux/Unix system (proficient)\\ 
{\sl \textbf{Machine Learning:}} Keras, sklearn, Tensorflow, PyTorch\\ 
{\sl \textbf{Databases:}} MySQL, MongoDB, Firebase\\
{\sl \textbf{Web Technology:}}  HTML5 (proficient), Vue.JS (prior experience), Django (prior experience), ReactJS(familiar)\\
{\sl \textbf{Other Tools:}}  Git(proficient), Arduino (prior experience), \LaTeX
 \vspace{-2mm}

\section{Projects}
\textbf{Realtime Face Recognition using Neural Networks (Tensorflow on Python)}\hfill Jan '18 – Apr '18\\
\begin{itemize}
  \vspace{-2mm}
 \item Implemented a Convolution Neural Network(InceptionV3) for face recognition.
 \item Achieved an accuracy of 97.8\% on a sparse dataset(1500 samples across 83 classes).
 \item Tested the system's application as an automated real time attendance system in classroom environments.
\end{itemize}

\textbf{Toxic Comment Classification (Python, Kaggle)}
\hfill Mar '18 – Apr '18\\
\begin{itemize}
  \vspace{-2mm}
 \item Took part in a Kaggle competition based on text classification for comments.
 \item Used extensive feature engineering and Ensemble ML models to score in 70th percentile.
 \item Achieved validation accuracy of  97\%.
 \end{itemize}

\textbf{Panchi, a Twitter like micro-blogging service (Django/Python)}
\hfill Jan '17 – Apr '17\\
\begin{itemize}
  \vspace{-2mm}
 \item Undertook this project as a part of my University Curriculum for Database Management.
 \item Used Database messaging and websockets for instant notifications and updates.
 \item Developed using Django to handle data at a larger scale.
 \end{itemize}

\textbf{Sensor Hive Network (C/Arduino)}
\hfill Jan '16 – Mar '16\\
\begin{itemize}
  \vspace{-2mm}
 \item Designed this IoT project to collect various weather data(temperature, humidity, etc) on Arduino.
 \item Used ThinkSpeak to collect and perform analysis and predict weather conditions on the data.
 \end{itemize}

\textbf{Tekken (NodeJS) \url{(https://github.com/shbm/tekken)}
}\hfill Mar '15 – Jun '15\\
\begin{itemize}
  \vspace{-2mm}
 \item Scraped wikipedia pages of famous TV shows to generated fake data.
 \item Wrote tests that covered continuous testing and continuous integration.
 \item Used by around 1200 NodeJS developers.
 \end{itemize}


\section{Experience}
\textbf{Cultural and Technical Festival, Manipal University Jaipur}\newline
 - {\sl Web Developer} \hfill Sep '16 – Apr '17\\
 \vspace{-2mm}
 \begin{itemize}
 \item Designed management and registration system for attendees from 27 colleges taking part in 45 events, using LAMP stack and Cloudflare hosting
 \item Handled more than 500 requests/second on peak traffic.
 \end{itemize}

   \vspace{-2mm}

\section{Education}
{\sl Bachelor of Technology} - Manipal University Jaipur,  Information Technology (7.17)\hfill Expected: May '19\\
  \vspace{-2mm}

\section{Relevant Coursework}
  {\sl Machine Learning}: Deep Learning for Coders, fast.ai(MOOC), Introduction to Machine Learning(MOOC), Convolution Neural Networks by Andrej Karpathy, Stanford(MOOC)\\
  {\sl Computer Science}: Data Structures and Algorithms using C, Database Management Systems, Operating Systems, Computer Networks


\end{resume}
\end{document}



